Coexistence with varying environmental filtering intensity

### 2018-07-06 env_intensity.Rmd
:sparkles: Compute all possible scenarios with 3 traits

# Simulations ------------------------------------------------------------------
three_traits <- multigen(traits = traits,
                         trait_type = trait_types,
                         env = env,
                         time = time,
                         species = species,
                         patches = patches,
                         composition = composition,
                         A = A, d = d,
                         k = k, width = width)

@@

# Plot individual patches 
plot_single_patch <- directlabels::direct.label(plot_patch(three_traits$compo,
                                                           1, 150))

# Plot species richness
nb_ind_final <- three_traits$compo[,,time]
sp_rich_final <- rowSums(nb_ind_final > 2)

@@

```{r}
all_land = landscape_df(three_traits, trait_types) %>%
    inner_join(traits %>%
                   as.data.frame() %>%
                   rownames_to_column("species"),
               by = "species") %>%
    group_by(patch) %>%
    mutate(rel_abund = N/sum(N)) %>%
    ungroup() %>%
    gather("trait_name", "trait_value", contains("trait"), optim_env)

# data.frame containing CWM values for all the traits, as well as growth-related
# traits (optim_env) for each patch and each simulation scenario
cwm_patch_trait = all_land %>%
    group_by(patch, trait_name) %>%
    summarise(cwm_trait = sum(rel_abund*trait_value),
              patch_optim = mean(patch_optim))

# Plot of Trait CWM in function of environmental value, colored by scenario
plot_cwm = ggplot(cwm_patch_trait, aes(patch_optim, cwm_trait)) +
    geom_abline(slope = 1, intercept = 0, linetype = 2) +
    geom_point(size = 1.5) +
    geom_smooth(method = "lm", se = FALSE) +
    facet_wrap(~trait_name, ncol = 3) +
    labs(x     = "Environmental Value",
         y     = "CWM of Trait",
         color = "Scenario") +
    theme_bw() +
    theme(legend.key.height = unit(2, "lines"))
plot_cwm

# Plot showing the number of individuals at t=150 for each trait and each
# environmental value
plot_individuals_trait_environment = all_land %>%
    ggplot(aes(trait_value, patch_optim)) +
    stat_summary_2d(aes(z = N)) +
    facet_grid(trait_name ~ .) +
    scale_fill_viridis_c(trans = "log10") +
    labs(x = "Trait Value",
         y = "Optimal Trait Value",
         fill = "Number of Individuals") +
    theme_bw()

>>>>

# Generate all possible scenarios with combinations of influence from RA trait
multiple_scenarios = expand.grid(c(0.2, 0.5, 0.8), c(0.2, 0.5, 0.8)) %>%
    rename(growth_weight = Var1,
           compet_weight = Var2) %>%
    mutate(trait = "trait2",
           scenario_name = paste0("RA", 100*growth_weight, 100*compet_weight)) %>%
    apply(1, function(y) {
        rbind(data.frame(trait = "trait1",
                         growth_weight = 1 - as.numeric(y[1]),
                         compet_weight = 0,
                         stringsAsFactors = FALSE),
              y[c(3, 1, 2)],
              data.frame(trait = "trait3",
                         growth_weight = 0,
                         compet_weight = 1 - as.numeric(y[2]),
                         stringsAsFactors = FALSE)) %>%
            cbind(scenario_name = rep(y[4], 3))
    }) %>%
    bind_rows()

# Simulations ------------------------------------------------------------------
three_traits <- lapply(
    trait_types, function(x) {
        multigen(traits = traits,
                 trait_weights = x,
                 env = env,
                 time = time,
                 species = species,
                 patches = patches,
                 composition = composition,
                 A = A, d = d,
                 k = k, width = width)
    })

@@

# Plot individual patches 
plot_single_patch <- lapply(
    three_traits, function(x) {
        directlabels::direct.label(plot_patch(x$compo, 1, 150))
    })

plot_grid(plotlist = plot_single_patch, ncol = 3)

# Plot species richness
# nb_ind_final <- three_traits$compo[,,time]
# sp_rich_final <- rowSums(nb_ind_final > 2)

@@

```{r}
all_land = lapply(names(three_traits), function(scenario) {
    landscape_df(three_traits[[scenario]], trait_types[[scenario]]) %>%
    inner_join(traits %>%
                   as.data.frame() %>%
                   rownames_to_column("species"),
               by = "species") %>%
    group_by(patch) %>%
    mutate(rel_abund = N/sum(N)) %>%
    ungroup() %>%
    gather("trait_name", "trait_value", contains("trait"), optim_env)
}) %>%
    set_names(nm = names(three_traits)) %>%
    bind_rows(.id = "scenario")

# data.frame containing CWM values for all the traits, as well as growth-related
# traits (optim_env) for each patch and each simulation scenario
cwm_patch_trait = all_land %>%
    group_by(scenario, patch, trait_name) %>%
    summarise(cwm_trait = sum(rel_abund*trait_value),
              patch_optim = mean(patch_optim))

# Plot of Trait CWM in function of environmental value, colored by scenario
plot_cwm = ggplot(cwm_patch_trait, aes(patch_optim, cwm_trait,
                                       color = scenario)) +
    geom_abline(slope = 1, intercept = 0, linetype = 2) +
    geom_point(size = 1.5) +
    geom_smooth(method = "lm", se = FALSE) +
    facet_wrap(~trait_name, ncol = 3) +
    labs(x     = "Environmental Value",
         y     = "CWM of Trait",
         color = "Scenario") +
    theme_bw() +
    theme(legend.key.height = unit(2, "lines"))
plot_cwm

# Plot showing the number of individuals at t=150 for each trait and each
# environmental value
plot_individuals_trait_environment = all_land %>%
    ggplot(aes(trait_value, patch_optim)) +
    stat_summary_2d(aes(z = N)) +
    facet_grid(trait_name ~ scenario) +
    scale_fill_viridis_c(trans = "log10") +
    labs(x = "Trait Value",
         y = "Optimal Trait Value",
         fill = "Number of Individuals") +
    theme_bw()
